Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-10 paper/paper.tex
fixes

Recall that a warning can be manifested for reasons other than a bug
and there is no clear way to distinguish those cases automatically (see
Table~\ref{tab:false-positives}). A human needs to inspect the warning
to diagnose the discrepancy. To facilitate inspection, the
infrastructure prioritize these warnings and clusters them in
groups. Considering prioritization, we classified warnings in two
kinds, reflecting their likelihood to manifest a real bug. Warnings of
the kind ``\hi{}'' are associated with the cases where the test code
executed to completion without violating any internal checks but it
violated assertions declared in the test itself or its harness. The
rationale is that the input is valid--considering the checks declared
in the API functions--but, still, it manifests discrepancy through
violation of an assertion declared in the test.\Mar{example!} In contrast, warnings
in the ``\lo{}'' group reflect the cases where the anomaly was
observed during the execution of functions not related to the test
itself. We found that different engines often check pre-conditions of
those functions differently. It can happen, for example, that one
engine enforces a weaker pre-condition on a function input compared to
another engine and that is acceptable.\Mar{example!} In those cases, our infrastructure would
observe a discrepancy that is more likely to be associated with an
invalid input produced by the fuzzer, \ie{}, it is likely to be a bug
in the test code not the engine (library or runtime) code. Although we
did find real bugs from ``\lo{}'' warnings, the proportion was much
lower compared to ``\hi{}'' warnings. Overall, only \Fix{12\%} of the
reals bugs we found originated from ``\lo{}'' warnings.

>>>>

Recall that a warning can be manifested for reasons other than a bug
and there is no clear way to distinguish those cases automatically (see
Table~\ref{tab:false-positives}). A human needs to inspect the warning
to diagnose the discrepancy. To facilitate inspection, the
infrastructure prioritize these warnings and clusters them in
groups. Considering prioritization, we classified warnings in two
kinds, reflecting their likelihood to manifest a real bug. Warnings of
the kind ``\hi{}'' are associated with the cases where the test code
executed to completion without violating any internal checks but it
violated assertions declared in the test itself or its harness. The
rationale is that the input is valid--considering the checks declared
in the API functions--but, still, it manifests discrepancy through
violation of an assertion declared in the test.\Mar{example!} In contrast, warnings
in the ``\lo{}'' group reflect the cases where the anomaly was
observed during the execution of functions not related to the test
itself. We found that different engines often check pre-conditions of
those functions differently. It can happen, for example, that one
engine enforces a weaker pre-condition on a function input compared to
another engine and that is acceptable.\Mar{example!} In those cases, our infrastructure would
observe a discrepancy that is more likely to be associated with an
invalid input produced by the fuzzer, \ie{}, it is likely to be a bug
in the test code not the engine (library or runtime) code. Although we
did find real bugs from ``\lo{}'' warnings, the proportion was much
lower compared to ``\hi{}'' warnings. Overall, only \Fix{12\%} of the
reals bugs we found originated from ``\lo{}'' warnings.
\Igor{
  Apesar dos bugs encontrados serem em sua maioria classificados como HI group,
  casos reportados como LO tambem podem ser considerados como um true positive.
  Nossa heuristica de classificacao eh baseada no error stream dos engenhos,
  se um teste falha antes da linha em que ha uma assercao, entao a falha
  ocorreu em uma funcao nativa do JS. Na figura \ref{fig:lo-truepositive}, \'e 
  possivel observar um caso de bug obtido em um bucket classificado como LO.
  Neste exemplo, o teste instancia um ArrayBuffer e armazena um 8-bit integer na 
  posicao 0 do dataframe, quando tentamos obter um elemento em uma posicao
  maior e/ou menor do que a suportada, neste caso \CodeIn{getInt8}, 
  de acordo com a especificacao\cite{ecmas262-getviewvalue}, deve-se 
  lancar Offset is outside the bounds.

  Os casos reportados no grupo LO nao foram capturados atraves das assercoes.
  Por exemplo, se o fuzzer gera uma entrada que viola uma especificacao, o 
  correto seria usar um levantar um erro
}

\begin{figure}[!h]
  \centering
  \begin{lstlisting}
    var buffer = new ArrayBuffer(64);
    var view = new DataView(buffer);
    view.setInt8(0,0x80);
    assert(view.getInt8(-1770523502845470856) === -0x80);

    Outputs:
    #### V8
    RangeError: Offset is outside the bounds of the DataView
    #### Chakra
    RangeError: DataView operation access beyond specified buffer length
    #### SpiderMonkey
    RangeError: invalid or out-of-range index
    #### JavaScriptCore
    RangeError: byteOffset cannot be negative
  \end{lstlisting}
  \caption{\label{fig:lo-truepositive}True positive example in LO warnings.}
\end{figure}
